---
title: "Lab4"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab4}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# How to use package

## Install
You can install with pak::pak.
```{r}
pak::pak("albba064/Lab4")
```

## Linreg
Fits a linear regression model where the regression coefficients and their variance are calculated using a QR decomposition of the design matrix.
```{r setup}
library(Lab4)
```
```{r}
data(iris)

model <- linreg(Petal.Length ~ Sepal.Width + Sepal.Length, iris)
```

## Print method
Prints the function call and estimated regression coefficients from a $\code{linreg}$ object.
```{r}
print(model)
```

## Plot method
Creates diagnostic plots for an object of class $\code{linreg}$. The function produces a Residuals vs Fitted plot and a Scale-Location plot using $\code{ggplot2}$.
```{r}
plt <- plot(model)
invisible(NULL)
```

## Resid method
Extracts the residuals from a $\code{linreg}$ object. Returns $\hat{e}$
```{r}
resid(model)
```

## Pred method
Extracts the fitted values from a $\code{linreg}$ object.
```{r}
pred(model)
```

## Coef method
Extracts the estimated regression coefficients from a $\code{linreg}$ object.
```{r}
coef(model)
```

## Summary method
Prints a summary of a $\code{linreg}$ object, including the estimated regression coefficients, standard errors, t-statistics, p-values, residual standard error, and residual degrees of freedom.
```{r}
summary(model)
```